Playing with PCAs

### 2024-03-15 3-reports/playing_with_pcas.Rmd
CV

>>>>

## CV

```{r}
cv = 
  data_combined %>% 
  group_by(region, site, transect, horizon, analysis, name) %>% 
  dplyr::summarise(cv = 100 * sd(value)/mean(value),
                   n = n(),
                   mean = mean(value)) %>% 
  filter(!transect %in% "wte")
```

```{r}
(cv %>% 
   filter(!(name == "Al_meq100g" & region == "WLE")) %>% 
  ggplot(aes(x = transect, y = cv))+
  geom_violin(scale = "area", fill = "grey90")+
  geom_jitter(width = 0.1, size = 3, aes(color = site, text = name))+
   geom_boxplot(width = 0.05, outlier.color = NA)+
  facet_wrap(~region)+
   theme_kp())  %>% plotly::ggplotly()

cv %>% 
  ggplot(aes(x = region, y = cv))+
  geom_point(width = 0.1, aes(color = transect), 
             position = position_dodge(width = 0.2))+
  expand_limits(y = 0)+
  facet_wrap(~ name, scales = "free_y")

View(data_combined_wide %>% dplyr::select(region, site, transect, horizon, contains(c("dic", "pH"))))
```
